Structural controllability of ecological networks

### 2018-06-28 paper/manuscript.Rmd
Improve caption of partial residuals plot

```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Partial-residual plots for the relationship between control capacity and the independent variables: (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree. Partial residual plots show the relationship between the response and each of the independent variables given that all other independent variables have been accounted for. Ploted values correpond to the predictions of the weighted average of the models shown in Table \\@ref(tab:tab-model-selection-table)"}
drake::loadd(fig_species_partial)
fig_species_partial %>%
  purrr::map_at(2:4, function(x) x  + theme(axis.title.y = element_blank(), axis.text.y = element_blank())) %>%
    cowplot::plot_grid(plotlist = ., align = "h", nrow = 1, rel_widths = c(1.25, 1, 1,1))
```

>>>>

```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Partial-residual plots for the independent variables: (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree. Partial-residual plots show the relationship between control capacity and each of the independent variables while acccounting for all other remaining variables. Ploted values correpond to the predictions of the weighted average of the models shown in Table \\@ref(tab:tab-model-selection-table)"}
drake::loadd(fig_species_partial)
fig_species_partial %>%
  purrr::map_at(2:4, function(x) x  + theme(axis.title.y = element_blank(), axis.text.y = element_blank())) %>%
    cowplot::plot_grid(plotlist = ., align = "h", nrow = 1, rel_widths = c(1.25, 1, 1,1))
```
